Motorcycle Acceleration example

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted magenta line).

```{r plot-homo-smash-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
#  lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
#        col = "darkblue")
#  lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

@@

*Add text here.*

>>>>

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted, light blue line).

```{r plot-homo-smash-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",
      col = "dodgerblue")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

@@

The TI thresholding estimate and the SMASH estimate with homoskedastic
variances both show notable artifacts. When the TI thresholding method
is provided with the SMASH variance estimates, the mean signal is much
more smooth.
